The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
blah

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougars
had increased home range overlap in regions with high hunting opportunity, a
proxy for resource richness [@Elbroch_2016]. Caribou showed seasonal differences
in sociality, where social associations were high in winter and contrastingly
low in summer when resource availability is homogenous [@Peigner_2019]. Bison
(*Bison bison*) showed stronger habitat selection when group size was larger and
avoidance of predation risk was a main factor contributing to their habitat
selection [@Fortin_2009]. <!--Despite these, *missing multilayer approach*.-->

Mayor 2007 - scale paper
MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, (3)
the habitat patches within the home range and (4) specific resources within a
habitat patch. Moving past this hierarchical perspective, Mayor (2009)
reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection. For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.

<!--
how to combine moving forward
multilayer networks across landcover types
in areas of high selection/low selection or favorable/unfavorable habitat
combined with seasonality

@@

conversely, one might envision generating a multilayer network where
nodes are individual patches
selection,
similarity, 
connectivity

How to combine moving forward: habitat selection, space use, multiple scales, multilayer networks
Sociality across scales eg home range overlap and interactions
Layers defined by habitat/landcover

Multilayer networks can be combined to consider habitat selection, across scales

Animal social systems can be parsed by spatial contexts, defined by habitat types or connectivity, each represented in a layer within a multilayer framework
Seasonality of resources can be directly measured by investigating differences in habitat selection and sociality between seasonal layers

Taken together, these novel and explicit integrations of habitat selection and space use in multilayer netwokr

>>>>

Mayor 2007 - scale paper
MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, (3)
the habitat patches within the home range and (4) specific resources within a
habitat patch. Moving past this hierarchical perspective, Mayor (2009)
reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection. For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougars
had increased home range overlap in regions with high hunting opportunity, a
proxy for resource richness [@Elbroch_2016]. Caribou showed seasonal differences
in sociality, where social associations were high in winter and contrastingly
low in summer when resource availability is homogenous [@Peigner_2019]. Bison
(*Bison bison*) showed stronger habitat selection when group size was larger and
avoidance of predation risk was a main factor contributing to their habitat
selection [@Fortin_2009]. These examples are implicitly multilayered, comparing sociality across contexts of seasonality or spatial context. <!--Despite these, *missing multilayer approach*.-->

<!--
how to combine moving forward
in areas of high selection/low selection or favorable/unfavorable habitat
combined with seasonality

@@

Multilayer networks can be used to explicitly consider habitat selection and sociality across scales. Animal social systems can be parsed by spatial contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres). The influence of resource phenology can be directly measured by differences in habitat selection and sociality across temporal layers. Habitat selection can be explicitly integrated using network layers defined by similarity of selection coefficients between individuals. These explicit integrations of habitat selection and sociality across social, spatial and temporal scales highlight the potential for novel insights from multilayer networks.
